Introduction

### 2018-04-30 ack.tex
thesis and presentation

I am also grateful to many students and research scientists I've had the pleasure of interacting with: 
Sean Bader, Luke Decker, Preston Fussee-Durham, Zhicheng Geng, Eric Goldfarb, Ben Gremillion, Tom Hess, Ken Ikeda, Harpreet Kaur, Dr. Dmitrii Merzlikin, Nam Pham, Mason Phillips, Kelly Regimbal, Karl Schleicher, Yunzhi Shi, Dr. Junzhe Sun, Dr. Yanadet Sripanich, Dr. Xinming Wu, Dr. Zhiguang Xue, and Dr. Yunan Yang.

>>>>

I am also grateful to many students and research scientists I've had the pleasure of interacting with: 
Sean Bader, Luke Decker, Preston Fussee-Durham, Zhicheng Geng, Eric Goldfarb, Ben Gremillion, Tom Hess, Ken Ikeda, Harpreet Kaur, Dmitrii Merzlikin, Nam Pham, Mason Phillips, Kelly Regimbal, Karl Schleicher, Yunzhi Shi, Dr. Junzhe Sun, Dr. Yanadet Sripanich, Dr. Xinming Wu, Dr. Zhiguang Xue, and Dr. Yunan Yang.

I would especially like to thank the members of the Texas Consortium for Computational Seismology (TCCS), of which I have been a part for the past two years.
%Thank you for all your guidance, and for being there for the best memories during my undergraduate career.
%Thank you for your intellectually stimulating conversations, life advice, and making me feel as though I am ``part of the group'', despite the fact that I was not a graduate student.
Thank you all for your intellectually stimulating conversations, life advice, and for including me as ``part of the group'', despite the fact that I was only an undergraduate student.
%You are an incredibly enjoyable and intellectually stimulating group, and I am glad I have had the opportunity to cross paths with all of you in life.
I will forever cherish the friendships and memories I have made with all of you during my time as a part of TCCS. %Many of the best memories of my time at UT Austin are from being a part of TCCS, %come from the %time I have spent as a part of TCCS.
You are an incredibly ingenuitive and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.

### 2018-04-30 chapter-background/paper.tex
thesis and presentation

\title{Background}
\author{Sarah Yvonne Greer}
\maketitle
\inputdir{../chapter-locfreq/merge}
Seismic data contain fundamentally non-stationary variations in attributes such as frequency and amplitude content.
For example, Figure \ref{fig:legacy,low-freq} shows a sample seismic image and its local frequency content \cite[]{locfreq}.
%Non-stationary, or spatially and temporally variant, changes in these data can make the comparison of two data sets difficult.
%These non-stationary variations mean that, in a given data set, different 
Data matching problems involve finding some transformation, or set of transformations, that can be applied to one data set to best match some attribute with another data set.
In data matching applications, in particular, it is crucial to acknowledge the non-stationary variations present in seismic data.
Therefore, any transformations we may apply in a data matching problem must be variant in all data dimensions to account for these non-stationary variations.

Local seismic attributes are useful in the analysis of these non-stationary variations that are naturally present in seismic data \cite{attr}.
The calculation of these attributes uses iterative inversion with shaping regularization \cite{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
For the procedures described in this thesis, local attributes are better-suited attributes than instantaneous attributes.
Take, for example, local frequency (Figure \ref{fig:legacy,low-freq}), as opposed to instantaneous frequency.
Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images. 
Because the corresponding reflections between images may not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency. 
Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or extremely high frequency values \cite[]{attr}.

@@

In this thesis, I propose solving data matching problems by balancing smoothly varying non-stationary attributes, such as local seismic attributes, between two data sets.
%local seismic attributes between data sets.
This is done using three primary data matching operations---filtering, scaling, and shifting---to effectively balance these attributes across seismic data sets.
These operations are applied to different data sets to correctly match them for analysis or further processing.

@@

\section{Filtering}
Perhaps one of the most visibly obvious differences between data sets comes from differences in frequency content.
For example, Figure \ref{fig:one0} shows two traces that need to be matched; the red trace has visibly higher frequency content than the black trace which makes it difficult to observe that they may both contain data from the same model.
This makes the correlation of these two signals, both visually and computationally, difficult as they have information in different frequency bands.
In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content with the black trace, since the high frequency content is not physically present in the black trace.

There are several ways to do this.
An naive first approach would be to apply a bandpass filter to the red trace such that the passband covers only frequencies that are present in the black trace.
However, this stationary operation does not take into account the non-stationary frequency variations that may be naturally present in the data.
In order to properly match the data in frequency content, we propose balancing local frequency content between data sets.

@@

\section{Scaling}
The second primary data matching operation is scaling. 
Amplitudes of the data we are trying to match may not be initially correct---scaling attempts to balance the amplitudes between these data.
Scaling is also a linear operation, and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.

In this thesis, the diagonal scaling operator is found by first calculating the amplitude envelope of the data that need to be matched.
Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces, and represent the diagonal elements of the scaling operator.
%The result of

@@

In this thesis, I calculate the shifting operator by finding the time shifts that maximize local similarity between the two data sets.
Local similarity extends the concept of local seismic attributes to global correlation coefficients, and is effective for measuring the match of seismic events in a local region of samples \cite[]{attr}.
Unlike filtering and scaling, shifting is a non-linear transformation.
%The time shift calculated is

In certain situations, these data must be correctly aligned in space instead of time; for example, in a depth-migrated image.
In these cases, {\em time} shift is a misnomer. 
However, since the data we are typically dealing with are time series, the shifting operation that we find and apply is considered a function of time.

@@

A summary of the three data matching operations is shown in Table \ref{op}.
Both scaling and filtering are linear operations, while shifting is generally a non-linear operation.
Additionally, as scaling is to weighting in the time domain, filtering is to weighting in the Fourier domain.
The next chapter discusses a few methods and examples of filtering, or frequency balancing, between two data sets.

>>>>

\title{Background}
\author{Sarah Yvonne Greer}
\maketitle
\inputdir{../chapter-locfreq/merge}
Seismic data contain fundamentally non-stationary variations in attributes such as frequency and amplitude content.
For example, Figure \ref{fig:legacy,low-freq} shows a sample seismic image and its local frequency content \cite[]{locfreq}.
%Non-stationary, or spatially and temporally variant, changes in these data can make the comparison of two data sets difficult.
%These non-stationary variations mean that, in a given data set, different 
Data matching problems involve finding some transformation, or set of transformations, that can be applied to one data set to best match some attribute with another data set.
In data matching applications, in particular, it is crucial to acknowledge the non-stationary variations present in seismic data.
Therefore, any transformations we might apply in a data matching problem must be variant in all data dimensions to account for these non-stationary variations.

Local seismic attributes are useful in the analysis of these non-stationary variations that are naturally present in seismic data \cite{attr}.
The calculation of these attributes uses iterative inversion with shaping regularization \cite{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
For the procedures described in this thesis, local attributes are more appropriate than instantaneous attributes.
Take, for example, local frequency (Figure \ref{fig:legacy,low-freq}), as opposed to instantaneous frequency.
Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images. 
Because the corresponding reflections between images might not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency. 
Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or extremely high frequency values \cite[]{attr}.

@@

In this thesis, I propose solving data matching problems by balancing smoothly varying non-stationary attributes, such as local seismic attributes, between two data sets.
%local seismic attributes between data sets.
This is done using three primary data matching operations---filtering, scaling, and shifting---to effectively balance these attributes across seismic data sets.
These operations are applied to different data sets to match them correctly for analysis or further processing.

@@

\section{Filtering}
Perhaps one of the most visibly obvious differences between data sets comes from differences in frequency content.
For example, Figure \ref{fig:one0} shows two traces that need to be matched; the red trace has visibly higher frequency content than the black trace which makes it difficult to observe that they may both contain data from the same model.
This makes the correlation of these two signals, both visually and computationally, difficult as they have information in different frequency bands.
In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content with the black trace because the high frequency content is not physically present in the black trace.

There are several ways to do this.
A na\"ive first approach would be to apply a bandpass filter to the red trace such that the passband covers only frequencies that are present in the black trace.
However, this stationary operation does not take into account the non-stationary frequency variations that may be naturally present in the data.
In order to properly match the data in frequency content, we propose balancing local frequency content between data sets.

@@

\section{Scaling}
The second primary data matching operation is scaling. 
Amplitudes of the data we are trying to match may not be initially correct---scaling attempts to balance the amplitudes between these data.
Scaling is also a linear operation and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.

In this thesis, the diagonal scaling operator is found by first calculating the amplitude envelope of the data that need to be matched.
Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces and represents the diagonal elements of the scaling operator.
%The result of

@@

In this thesis, I calculate the shifting operator by finding the time shifts that maximize local similarity between the two data sets.
Local similarity extends the concept of local seismic attributes to global correlation coefficients and is effective for measuring the match of seismic events in a local region of samples \cite[]{attr}.
Unlike filtering and scaling, shifting is a non-linear transformation.
%The time shift calculated is

In certain situations, these data must be correctly aligned in space instead of time; for example, in a depth-migrated image.
In these cases, {\em time} shift is a misnomer. 
However, because the data we are typically dealing with are time series, the shifting operation that we find and apply is considered a function of time.

@@

A summary of the three data matching operations is shown in Table \ref{op}.
Both scaling and filtering are linear operations, whereas shifting is generally a non-linear operation.
Additionally, as scaling is to weighting in the time domain, filtering is to weighting in the Fourier domain.
The next chapter discusses a few methods and examples of filtering, or frequency balancing, between two data sets.

### 2018-04-30 chapter-conclusion/paper.tex
thesis and presentation

In this thesis, I discussed several methods and applications of data matching in seismic data analysis.

Chapter 2 focuses on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.

Chapter 3 introduces different methods of frequency balancing using non-stationary smoothing. 
The first method to find the non-stationary smoothing {\em radius}, or number of samples each data point is averaged over with a triangle weight, took a theoretical approach based off of the assumption that the data we observe can be modeled by a summation of Ricker wavelets.
This method worked well in certain situations, but was not robust enough to work for any given data set.
In the second method, I introduced an iterative algorithm to find the smoothing radius, and this method converges quickly and works well in several presented situations. 
Finally, a modification to this algorithm was shown and allows smoothing for more complex data sets.

@@

Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
An approximation to the least-squares Hessian can calculated by solving a data matching problem between two conventionally migrated images, and can be represented by the combination of amplitude and frequency balancing operations.
An example is applied to a 2D synthetic Sigsbee data set.

@@

Another extension of this data matching procedure may be to incorporate
%Another component to data matching may incorporate 
the phase of the signal to be matched. 
Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems may benefit from these corrections.

Several applications of data matching were discussed in this thesis. 
However, there are still many applications that may remain unaddressed from a data matching standpoint. 
Problems such as seismic and well-log tying, deconvolution, automatic gain control (AGC), and surface-related multiple elimination (SRME) can also be recast as data matching problems, and looking at these problems in a new light may bring advancements to computational geophysics.

@@

\begin{table}[h]
\centering
\caption{Figures and the scripts to generate them}
\label{my-label}
\begin{tabular}{l|l|l}
\hline
        \textbf{Figures} & \textbf{Directory} & \textbf{Listings} \\ \hline 
        \ref{fig:legacy,low-freq} & chapter-locfreq/merge/ & \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:one0,one1,one2,one3}, \ref{fig:bef,aft} & chapter-background/dmExample/ & \ref{lst:dm} \\ 
        \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, \ref{fig:freqdif,freqdif-filt}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
        \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, \ref{fig:freqdif,freqdif-filt5}          & chapter-locfreq/merge/ &   \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:pp,ss}, \ref{fig:before,after}         & chapter-locfreq/vecta/&  \ref{lst:lvs}, \ref{lst:lvn}, \ref{lst:lvrp}, \ref{lst:lvrc}\\ 
        \ref{fig:all,scalar} & chapter-locfreq/convergence/&  \ref{lst:conv}\\ 
        \ref{fig:legacy,hires,merge2-reverse}, \ref{fig:diff0,diff1}, \ref{fig:hweight,lweight-reverse}, \ref{fig:nspectra22-reverse}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
        \ref{fig:window1,window2}, \ref{fig:nspectra2} & chapter-merge/pcable/ & \ref{lst:mps} \\ 
        \ref{fig:legacy4,hires4,merge3}  & chapter-merge/pcable2/ & \ref{lst:mp2s}, \ref{lst:mp2rp}, \ref{lst:mp2rc}\\ 
        \ref{fig:mod,vel-migration}, \ref{fig:image0,image1}, \ref{fig:a0,rect10b}, \ref{fig:migdec-shap}, \ref{fig:image0-w3,migdec-w3,mod-w3} & chapter-merge/mighes/ & \ref{lst:hss}, \ref{lst:hsrp}, \ref{lst:hsrc}\\ 
        \ref{fig:tf}, & chapter-merge/triop/ & \ref{lst:triop}, \ref{lst:trfu} \ref{lst:solve}\\ 
\end{tabular}
\end{table}

\subsection{Chapter 2}

\lstinputlisting[label={lst:dm},caption={chapter-background/dmExample/dmExample.py}]{../chapter-background/dmExample/dmExample.py}

\subsection{Chapter 3}
%
%\inputdir{../chapter-locfreq/merge}
%This chapter is split into three main projects (directories). 
%
%\inputdir{../chapter-merge/apache}
%The code to generate Figures \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, and \ref{fig:freqdif,freqdif-filt}, which are used to demonstrate the theoretical smoothing radius, is contained with the code for Chapter 4.
%
%The second project is in the merge directory and includes the example with of the iterative algorithm to balance local frequency content between data sets.
%This includes the code to generate Figures \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, and \ref{fig:freqdif,freqdif-filt5}.
%
%The third project demonstrates the 
\lstinputlisting[label={lst:lms},caption={chapter-locfreq/merge/SConstruct}]{../chapter-locfreq/merge/SConstruct}
\lstinputlisting[label={lst:lmrp},caption={chapter-locfreq/merge/radius.py}]{../chapter-locfreq/merge/radius.py}
\lstinputlisting[language=C,label={lst:lmrc},caption={chapter-locfreq/merge/radius.c}]{../chapter-locfreq/merge/radius.c}

\lstinputlisting[label={lst:lvs},caption={chapter-locfreq/vecta/SConstruct}]{../chapter-locfreq/vecta/SConstruct}
\lstinputlisting[label={lst:lvn},caption={chapter-locfreq/vecta/newwarplocfreq.py}]{../chapter-locfreq/vecta/newwarplocfreq.py}
\lstinputlisting[label={lst:lvrp},caption={chapter-locfreq/vecta/radius2.py}]{../chapter-locfreq/vecta/radius2.py}
\lstinputlisting[label={lst:lvrc},language=C,caption={chapter-locfreq/vecta/radius2.c}]{../chapter-locfreq/vecta/radius2.c}

\lstinputlisting[label={lst:conv},caption={chapter-locfreq/convergence/plot.py}]{../chapter-locfreq/convergence/plot.py}

\subsection{Chapter 4}
\lstinputlisting[label={lst:mas},caption={chapter-merge/apache/SConstruct}]{../chapter-merge/apache/SConstruct}
\lstinputlisting[label={lst:mps},caption={chapter-merge/pcable/SConstruct}]{../chapter-merge/pcable/SConstruct}
\lstinputlisting[label={lst:mp2s},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/SConstruct}
\lstinputlisting[label={lst:mp2rp},caption={chapter-merge/pcable2/radius.py}]{../chapter-merge/pcable2/radius.py}
\lstinputlisting[language=C,label={lst:mp2rc},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/radius.c}

\subsection{Chapter 5}
\lstinputlisting[label={lst:hss},caption={chapter-mighes/sigsbee/SConstruct}]{../chapter-mighes/sigsbee/SConstruct}
\lstinputlisting[label={lst:hsrp},caption={chapter-mighes/sigsbee/radius.py}]{../chapter-mighes/sigsbee/radius.py}
\lstinputlisting[language=C,label={lst:hsrc},caption={chapter-mighes/sigsbee/radius.c}]{../chapter-mighes/sigsbee/radius.c}

\lstinputlisting[label={lst:triop},caption={chapter-mighes/triop/triOp.py}]{../chapter-mighes/triop/triOp.py}
\lstinputlisting[label={lst:trfu},caption={chapter-mighes/triop/trfu.py}]{../chapter-mighes/triop/trfu.py}
\lstinputlisting[label={lst:solve},caption={chapter-mighes/triop/solve.py}]{../chapter-mighes/triop/solve.py}

>>>>

In this thesis, I discussed several methods and applications of data matching in seismic data analysis.
Chapter 2 focuses on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.
Chapter 3 introduces different methods of frequency balancing using non-stationary smoothing. 
The first method to find the non-stationary smoothing {\em radius}, or number of samples each data point is averaged over with a triangle weight, took a theoretical approach based off of the assumption that the data we observe can be modeled by a summation of Ricker wavelets.
This method worked well in certain situations, but was not robust enough to work for any given data set.
In the second method, I introduced an iterative algorithm to find the smoothing radius, and this method converges quickly and works well in several presented situations. 
Finally, a modification to this algorithm was shown and allows smoothing for more complex data sets.

@@

Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
An approximation to the least-squares Hessian can be calculated by solving a data matching problem between two conventionally migrated images, and the Hessian can be represented by the combination of amplitude and frequency balancing operations.
An example is applied to a 2D synthetic Sigsbee data set.

@@

Another extension of this data matching procedure may be to incorporate
%Another component to data matching may incorporate 
the phase of the signal to be matched. 
Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems could benefit from these corrections.

Several applications of data matching were discussed in this thesis. 
However, many applications remain unaddressed from a data matching standpoint. 
Problems such as seismic and well-log tying, deconvolution, automatic gain control (AGC), and surface-related multiple elimination (SRME) can also be recast as data matching problems. Looking at these problems in a new light may bring advancements to computational geophysics.

@@

\begin{table}[h]
\centering
\caption{Figures and the scripts to generate them}
\label{my-label}
\begin{tabular}{l|l|l}
\hline
        \textbf{Figures} & \textbf{Directory} & \textbf{Listings} \\ \hline 
        \ref{fig:legacy,low-freq} & chapter-locfreq/merge/ & \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:one0,one1,one2,one3}, \ref{fig:bef,aft} & chapter-background/dmExample/ & \ref{lst:dm} \\ 
        \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, \ref{fig:freqdif,freqdif-filt}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
        \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, \ref{fig:freqdif,freqdif-filt5}          & chapter-locfreq/merge/ &   \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
        \ref{fig:pp,ss}, \ref{fig:before,after}         & chapter-locfreq/vecta/&  \ref{lst:lvs}, \ref{lst:lvn}, \ref{lst:lvrp}, \ref{lst:lvrc}\\ 
        \ref{fig:all,scalar} & chapter-locfreq/convergence/&  \ref{lst:conv}\\ 
        \ref{fig:legacy,hires,merge2-reverse}, \ref{fig:diff0,diff1}, \ref{fig:hweight,lweight-reverse}, \ref{fig:nspectra22-reverse}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
        \ref{fig:window1,window2}, \ref{fig:nspectra2} & chapter-merge/pcable/ & \ref{lst:mps} \\ 
        \ref{fig:legacy4,hires4,merge3}  & chapter-merge/pcable2/ & \ref{lst:mp2s}, \ref{lst:mp2rp}, \ref{lst:mp2rc}\\ 
        \ref{fig:mod,vel-migration}, \ref{fig:image0,image1}, \ref{fig:a0,rect10b}, \ref{fig:migdec-shap}, \ref{fig:image0-w3,migdec-w3,mod-w3} & chapter-merge/mighes/ & \ref{lst:hss}, \ref{lst:hsrp}, \ref{lst:hsrc}\\ 
        \ref{fig:tf}, & chapter-merge/triop/ & \ref{lst:triop}, \ref{lst:trfu} \ref{lst:solve}\\ 
\end{tabular}
\end{table}
For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in chapter 3.

%\subsection{Chapter 2}
%
%\lstinputlisting[label={lst:dm},caption={chapter-background/dmExample/dmExample.py}]{../chapter-background/dmExample/dmExample.py}
%
%\subsection{Chapter 3}
%
%\inputdir{../chapter-locfreq/merge}
%This chapter is split into three main projects (directories). 
%
%\inputdir{../chapter-merge/apache}
%The code to generate Figures \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, and \ref{fig:freqdif,freqdif-filt}, which are used to demonstrate the theoretical smoothing radius, is contained with the code for Chapter 4.
%
%The second project is in the merge directory and includes the example with of the iterative algorithm to balance local frequency content between data sets.
%This includes the code to generate Figures \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, and \ref{fig:freqdif,freqdif-filt5}.
%
%The third project demonstrates the 
\lstinputlisting[label={lst:lms},caption={chapter-locfreq/merge/SConstruct}]{../chapter-locfreq/merge/SConstruct}
\lstinputlisting[label={lst:lmrp},caption={chapter-locfreq/merge/radius.py}]{../chapter-locfreq/merge/radius.py}
\lstinputlisting[language=C,label={lst:lmrc},caption={chapter-locfreq/merge/radius.c}]{../chapter-locfreq/merge/radius.c}

%
%
%\lstinputlisting[label={lst:lvs},caption={chapter-locfreq/vecta/SConstruct}]{../chapter-locfreq/vecta/SConstruct}
%\lstinputlisting[label={lst:lvn},caption={chapter-locfreq/vecta/newwarplocfreq.py}]{../chapter-locfreq/vecta/newwarplocfreq.py}
%\lstinputlisting[label={lst:lvrp},caption={chapter-locfreq/vecta/radius2.py}]{../chapter-locfreq/vecta/radius2.py}
%\lstinputlisting[label={lst:lvrc},language=C,caption={chapter-locfreq/vecta/radius2.c}]{../chapter-locfreq/vecta/radius2.c}
%
%\lstinputlisting[label={lst:conv},caption={chapter-locfreq/convergence/plot.py}]{../chapter-locfreq/convergence/plot.py}
%
%
%\subsection{Chapter 4}
%\lstinputlisting[label={lst:mas},caption={chapter-merge/apache/SConstruct}]{../chapter-merge/apache/SConstruct}
%\lstinputlisting[label={lst:mps},caption={chapter-merge/pcable/SConstruct}]{../chapter-merge/pcable/SConstruct}
%\lstinputlisting[label={lst:mp2s},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/SConstruct}
%\lstinputlisting[label={lst:mp2rp},caption={chapter-merge/pcable2/radius.py}]{../chapter-merge/pcable2/radius.py}
%\lstinputlisting[language=C,label={lst:mp2rc},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/radius.c}
%
%
%\subsection{Chapter 5}
%\lstinputlisting[label={lst:hss},caption={chapter-mighes/sigsbee/SConstruct}]{../chapter-mighes/sigsbee/SConstruct}
%\lstinputlisting[label={lst:hsrp},caption={chapter-mighes/sigsbee/radius.py}]{../chapter-mighes/sigsbee/radius.py}
%\lstinputlisting[language=C,label={lst:hsrc},caption={chapter-mighes/sigsbee/radius.c}]{../chapter-mighes/sigsbee/radius.c}
%
%\lstinputlisting[label={lst:triop},caption={chapter-mighes/triop/triOp.py}]{../chapter-mighes/triop/triOp.py}
%\lstinputlisting[label={lst:trfu},caption={chapter-mighes/triop/trfu.py}]{../chapter-mighes/triop/trfu.py}
%\lstinputlisting[label={lst:solve},caption={chapter-mighes/triop/solve.py}]{../chapter-mighes/triop/solve.py}

### 2018-04-30 chapter-intro/paper.tex
thesis and presentation

%Data matching problems are prevalent in many applications of seismic data processing.
Data matching is a conceptually simple problem that is present in many computational geophysics applications. 
Essentially, given two data sets, data matching can be thought of as finding the transformation from one data set to the other. 
This is useful in applications such as multi-component seismic image registration, where two separate seismic images, one P-wave image and one S- wave image, are acquired over the same area. 
These must be properly matched, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted. 
%Many other examples of data matching are prevalent in geophysical applications, such as time-lapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.

Many other geophysics applications can be addressed from a data matching standpoint, and fall under a few main categories.
Applications are present for data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in chapter 3.
Other problems consist of matching differently acquired data, such time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in chapter 4.
Data matching problems are also present for matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in chapter 5.
An approach to these many data matching problems is to find the operation to match the data using a combination of three data matching operations---filtering, scaling, and shifting.
%In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
In this thesis, I will discuss these three data matching operators, outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.

%However, many data matching algorithms, such as Dynamic Time Warping, can be computationally expensive, especially when applied to large multi-dimensional seismic data sets.
The primary inspiration for much of the work in this thesis comes from the example of matching and merging high-resolution and legacy seismic images, as discussed in \cite{merge2} and \cite{merge}.
In this example, two seismic data sets, each acquired over the same area but with different technologies, are first matched in frequency, amplitude, and time, before being merged together to produce a third image.
This new image includes the best signal characteristics from the two initial images while minimizing their weaknesses.
Much of the theory behind Chapter 3 was developed in application to this example, but was later extended to other examples.
As a result, I will be using data from this application throughout much of this thesis.

This thesis contains two primary data sets that I will be referring to. 
The first pair, henceforth called the {\it Apache} data sets, are two 2D lines, acquired over the same area but with different methods, from the Gulf of Mexico. 
These two images will always be plotted in the {\em seismic} color map.

The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable,data}.
These two images will always be plotted in grayscale.
In parts of this thesis, I will show a 2D line from this 3D data set for simplicity of plotting.

Two other data sets, both 2D, were used in this paper. 
In chapter 3, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
In chapter 5, I use the Sigsbee synthetic data set \cite[]{sigsbee} in application of improving migration resolution using non-stationary matching.

>>>>

%Data matching problems are prevalent in many applications of seismic data processing.
Data matching is a conceptually simple problem that is present in many computational geophysics applications. 
Essentially, given two data sets, data matching can be thought of as finding the transformation from one data set to the other. 
This is useful in applications such as multi-component seismic image registration, where two separate seismic images, one P-wave image and one S- wave image, are acquired over the same area. 
These must be matched properly, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted. 
%Many other examples of data matching are prevalent in geophysical applications, such as time-lapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.

Many other geophysics applications can be addressed from a data matching standpoint and fall under a few main categories.
Applications are present for data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in chapter 3.
Other problems consist of matching differently acquired data, such as time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in chapter 4.
Data matching problems are also present for matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in chapter 5.
An approach to these many data matching problems is to find the operation to match the data using a combination of three data matching operations---filtering, scaling, and shifting.
%In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
In this thesis, I will discuss these three data matching operators, outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.

%However, many data matching algorithms, such as Dynamic Time Warping, can be computationally expensive, especially when applied to large multi-dimensional seismic data sets.
The primary inspiration for much of the work in this thesis comes from the example of matching and merging high-resolution and legacy seismic images, as discussed in \cite{merge2} and \cite{merge}.
In this example, two seismic data sets, each acquired over the same area but with different technologies, are first matched in frequency, amplitude, and time, before being merged together to produce a third image.
This new image includes the best signal characteristics from the two initial images while minimizing their weaknesses.
Much of the theory behind Chapter 3 was developed in application to this example but was later extended to other examples.
As a result, I use data from this application throughout much of this thesis.

This thesis contains two primary data sets to which I refer. 
The first pair, henceforth called the {\it Apache} data sets, are two 2D lines, acquired over the same area but with different methods, from the Gulf of Mexico. 
These two images will always be plotted in the {\em seismic} color map.

The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable,data}.
These two images will always be plotted in grayscale.
In parts of this thesis, I show a 2D line from this 3D data set for simplicity of plotting.

Two other data sets, both 2D, were used in this paper. 
In chapter 3, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
In chapter 5, I use the Sigsbee synthetic data set \cite[]{sigsbee} in the application of improving migration resolution using non-stationary matching.
